%کلمات کلیدی انگلیسی
\latinkeywords{Artificial intelligence, Self-driving cars, Deep learning, Semantic segmentation, Fast image semantic segmentation}
%چکیده انگلیسی

\en-abstract{
Autonomous vehicles require a precise understanding of their surroundings to make informed decisions and navigate safely in various environments. Semantic segmentation, from its inception, stands as one of the fundamental stages in the process of analyzing images and extracting useful information for decision-making in such systems. It plays a vital role in detecting environmental objects, enabling the accurate identification of various entities including roads, pedestrians, other vehicles, and obstacles. Deep learning methods have significantly improved semantic segmentation, surpassing traditional approaches in performance. This project delves into recent advancements in semantic image segmentation for autonomous vehicles using deep learning methods. We investigate various architectures of deep learning in the context of rapid semantic segmentation, comparing their strengths and weaknesses for the specific task of autonomous driving. Additionally, the datasets used for training and evaluating semantic segmentation models in this domain are scrutinized, employing them to assess different deep learning models. In conclusion, a summary of the examined models is provided, along with suggestions for future research aimed at enhancing the sustainability, efficiency, and general applicability of real-time semantic segmentation systems based on deep learning for autonomous vehicles.
}

\newpage
\thispagestyle{empty}
\begin{latin}
\section*{\LARGE\centering Abstract}

\een-abstract

\vspace*{.5cm}
{\large\textbf{Key Words:}}\par
\vspace*{.5cm}
\elatinkeywords
\end{latin}